### 2021-12-08 manuscript.tex
Fix a few typos and whitespace issues

Room 290 was cold and clean, a room that was designed either to impress or intimidate.  Which effect took precedence depended on the lighting.  On this occasion, every light in the room was burning.  There were three conference tables arranged in a U-shape, with a single seat placed at the top of the U.  There were small drink knapkins laid on the tables in front of each seat, and karafes of fresh water had been deposited at even intervals.  Jesse counted ten fifteen seats.  \emph{Full tribunal}, he thought, still puzzling over the choice of time and location.

@@

A slow but steady stream of people entered over the next few minutes.  The next to enter the room was a man in a sharp black suit.  He was carrying a stack of folders under one arm and tapping on his smart phone with the opposite hand.  He had the distinct air of a lawyer, and Jesse's suspicion was reinforced when a gray-haired man in a polo shirt followed him.  \emph{A stuffy old philosophy professor}, Jesse thought.  \emph{My accuser}.  There were only two seats left at the table, and the man fit the bill.

@@

``I'll admit that I'm not an unbiased party here.  But I think that this hearing, and the trial that may follow, is a waste of your time.  It's a waste of the university's time and resources.  I am aware of the circumstances that made the each of the charges possible.  The problem is that Mr. Shelby and Mr. Malda are looking for intent where there is none.  My office has accidentally thrown away records before, and we have a procedure to deal with it.  No documents are allowed to remain in the trash, and each trash bin is checked before it's taken away.  All documents that need to be discarded are shredded by a cross-cut shredder and then incinerated.  If something managed to make it out of the office intact, then it was an honest, but still unforgivable, mistake.  We owe it to our students to protect their personal records.  However, it sounds to me as though someone plucked a discarded document from our office and is now trying to argue that we did something horribly wrong.''

@@

Jesse nodded to the Ombudsman and returned to his seat.  There were fleeting glances between the tables at this point.  Jesse knew that he had hit the mark.  Even thought he couldn't offer any direct evidence for his arguments, he knew that he had sewn just enough doubt to cut the legs from Shelby's case.

@@

\indent NEW YORK - Hungarian student in his third year at New York University was arraigned last week on charges of extortion, espionage and obstruction of justice.  The student, whose name has not been released by the NYPD, is accused of working for a Mexican drug cartel and Hamas, a Palestinian political organization.  He was arrested in July during a joint police and FBI raid of an abandoned warehouse in the Bronx.  It was determined that the student had lived in the warehouse for his three years at NYU and was in the United States legally on a student visa.  At a press conference on Tuesday, NYPD chief of police Sam Blanczyk said that Immigrations and Customs Enforcement was working with Hungarian officials to determine how the student would be tried.

@@

``That's where you're wrong, Jesse.  Even if they don't have a personal connection, this student has been doing dirty work for crime rings for years.  He's in the business of taking orders, collecting his pay, and keeping his head down.  He won't be the one to pull a gun on you, but Shelby already made it clear that he knows where you work and how to get in touch with you.  And he knows that you can be buffaloed into giving up sensitive records\dots''.

@@

``Okay,'' the receptionist said.  ``I'll need to see government-issued identification for each of you----sorry, it's protocol---and then I will get someone out here to talk to you.''

@@

>>>>

Room 290 was cold and clean, a room that was designed either to impress or intimidate.  Which effect took precedence depended on the lighting.  On this occasion, every light in the room was burning.  There were three conference tables arranged in a U-shape, with a single seat placed at the top of the U.  There were small drink knapkins laid on the tables in front of each seat, and karafes of fresh water had been deposited at even intervals.  Jesse counted ten, maybe fifteen seats.  \emph{Full tribunal}, he thought, still puzzling over the choice of time and location.

@@

A slow but steady stream of people entered over the next few minutes.  The next to enter the room was a man in a sharp black suit.  He was carrying a stack of folders under one arm and tapping on his smartphone with the opposite hand.  He had the distinct air of a lawyer, and Jesse's suspicion was reinforced when a gray-haired man in a polo shirt followed him.  \emph{A stuffy old philosophy professor}, Jesse thought.  \emph{My accuser}.  There were only two seats left at the table, and the man fit the bill.

@@

``I'll admit that I'm not an unbiased party here.  But I think that this hearing, and the trial that may follow, is a waste of your time.  It's a waste of the university's time and resources.  I am aware of the circumstances that made each of the charges possible.  The problem is that Mr. Shelby and Mr. Malda are looking for intent where there is none.  My office has accidentally thrown away records before, and we have a procedure to deal with it.  No documents are allowed to remain in the trash, and each trash bin is checked before it's taken away.  All documents that need to be discarded are shredded by a cross-cut shredder and then incinerated.  If something managed to make it out of the office intact, then it was an honest, but still unforgivable, mistake.  We owe it to our students to protect their personal records.  However, it sounds to me as though someone plucked a discarded document from our office and is now trying to argue that we did something horribly wrong.''

@@

Jesse nodded to the Ombudsman and returned to his seat.  There were fleeting glances between the tables at this point.  Jesse knew that he had hit the mark.  Even though he couldn't offer any direct evidence for his arguments, he knew that he had sewn just enough doubt to cut the legs from Shelby's case.

@@

\indent NEW YORK - A Hungarian student in his third year at New York University was arraigned last week on charges of extortion, espionage and obstruction of justice.  The student, whose name has not been released by the NYPD, is accused of working for a Mexican drug cartel and Hamas, a Palestinian political organization.  He was arrested in July during a joint police and FBI raid of an abandoned warehouse in the Bronx.  It was determined that the student had lived in the warehouse for his three years at NYU and was in the United States legally on a student visa.  At a press conference on Tuesday, NYPD chief of police Sam Blanczyk said that Immigrations and Customs Enforcement was working with Hungarian officials to determine how the student would be tried.

@@

``That's where you're wrong, Jesse.  Even if they don't have a personal connection, this student has been doing dirty work for crime rings for years.  He's in the business of taking orders, collecting his pay, and keeping his head down.  He won't be the one to pull a gun on you, but Shelby already made it clear that he knows where you work and how to get in touch with you.  And he knows that you can be buffaloed into giving up sensitive records\dots''

@@

``Okay,'' the receptionist said.  ``I'll need to see government-issued identification for each of you---sorry, it's protocol---and then I will get someone out here to talk to you.''

@@

% Need a bigger paragraph break here
